% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\def\name{Roman Perehonchuk}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Job title: & \textbf{Java software engineer} \\
    Phone: & 38 (063) 756-65-41 \\
    Email: & \href{mailto:roman.peregonchuk@gmail.com}{\tt roman.peregonchuk@gmail.com} \\
  \end{tabular}
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Experiance: & 2010 - now \\
    Date of birth: & 15.10.1990 \\
    Skype: & roman.peregonchuk \\
  \end{tabular}
\end{minipage}

\section*{Professional summary}
\begin{itemize}
\item I am Software Engineer with more than five years experience with Java. In my spare time, I like to learn new languages and tools, such as functional programming, Clojure, Go, Docker, and Ansible.
\end{itemize}

\section*{Technologies}

\begin{itemize}
\item java8, groovy, spring boot, spock, kafka, storm, liquibase, mysql, couchbase, netflix oss(hystrix, archaius, eureka), python(scripting language), linux  
\end{itemize}

\section*{Employment}

\subsection*{Playtika Kyiv studio; Slotomania infra services, 2013--now.}

\begin{itemize}
\item {\normalsize Playtika rewards: }worked in a scrum team, was responsible for development and support system with more than six million daily users. Our team designed and developed from scratch three major features: playtika rewards, jackpot, sloto cards and participated in development large microservice system written in Java.
\item {\normalsize Jackpot: }worked in a scrum team, was responsible for development and support system with more than six million daily users. Our team designed and developed from scratch three major features: playtika rewards, jackpot, sloto cards and participated in development large microservice system written in Java.  
\item {\normalsize Slotocards: } worked in a scrum team, was responsible for development and support system with more than six million daily users. Our team designed and developed from scratch three major features: playtika rewards, jackpot, sloto cards and participated in development large microservice system written in Java.  
\item {\normalsize Segmentation: }service aimed to segment users on different criterias, for advanced a/b testing. Tasks: handle all users and business events (20k/second), implement expression dsl on groovy, design api for services and clients.
\end{itemize}

\subsection*{Playtika Vinnytsia studio; Ceasers casino, 2011--2013.}

\begin{itemize}
\item game server development
\end{itemize}

\subsection*{InnoVinn; BATM Foundation Classes, 2010--2011.}

\begin{itemize}
\item development managment tool for different telecom devices based on SNMP protocol
\end{itemize}

\section*{Education}

\begin{itemize}
  \item Master degree, Vinnitsa National Technical University, Faculty of Computer 
Systems and Automation
  \item Functional Programming Principles in Scala, Coursera
  \item Machine Learning, Coursera
  \item Cloud computing concepts part 1, Coursera
\end{itemize}

\end{document}
